WrapITK: Enhanced languages support\\ for the Insight Toolkit

### 2006-04-12 article/Article.tex
add more info about rpm packages
darcs-hash:20060412140251-2fc9d-fd487192e14648c319d7491857ffa284c169311a.gz

RPM packages for Mandriva Linux 2006 are available at \url{http://voxel.jouy.inra.fr/mdk/mima2}.

@@

External projects let the developer access some custom class with the target languages
and is a powerful way to extend WrapITK, test new wrapper, wrap more types, etc.
A nice side effect of wrappers, for contributions\footnote{A nice template for
contributions to the Insight Journal \cite{InsightJournalWebSite} which include the 
template code to build wrappers is available at
\url{http://voxel.jouy.inra.fr/darcs/contrib-itk/template/}. Just use the command
{\em darcs get http://voxel.jouy.inra.fr/darcs/contrib-itk/template/ contribName}
and edit the project name in the {\em CMakeLists.txt} file to
begin your new contribution.} for example, is to build {\em all}
the methods of the wrapped classes, and so to be sure everything builds as it should
\footnote{We have found and fixed numbers of bug in ITK while adding
more classes to WrapITK}.
In WrapITK, we used them to avoid managing switches if some dependencies or not
found: the project must found this dependencies or fail.

>>>>

RPM packages for Mandriva Linux 2006 are available at \url{http://voxel.jouy.inra.fr/mdk/mima2}.
To install WrapITK for mandriva linux 2006.0, just add a new media with the
command

\begin{verbatim}
urpmi.addmedia mima2-2006.0 http://voxel.jouy.inra.fr/mdk/mima2/2006.0/i586/
\end{verbatim}

and install the package you want with

\begin{verbatim}
urpmi python-itk
\end{verbatim}

This media also contain several packages which may be useful to use WrapITK,
and which are not available in mandriva linux 2006.0. Here is the full list:
\begin{itemize}
  \item \verb$cmake$
  \item \verb$itk-data$
  \item \verb$itk-doc$
  \item \verb$itk-examples$
  \item \verb$itkvtk-devel$
  \item \verb$libitk$
  \item \verb$libitk-devel$
  \item \verb$libvtk$
  \item \verb$libvtk-devel$
  \item \verb$libvtk-qt$
  \item \verb$python-itk$
  \item \verb$python-itk-numarray$
  \item \verb$python-itkvtk$
  \item \verb$python-vtk$
  \item \verb$tcl-itk$
  \item \verb$tcl-vtk$
  \item \verb$vtk-data$
  \item \verb$vtk-doc$
  \item \verb$vtk-examples$
  \item \verb$vtk-test-suite$
  \item \verb$wrapitk-devel$
\end{itemize}

WrapITK is also available in cooker, the development version of mandriva.

@@

External projects let the developer access some custom class with the target languages
and is a powerful way to extend WrapITK, test new wrapper, wrap more types, etc.
A nice side effect of wrappers, for contributions\footnote{A nice template for
contributions to the Insight Journal \cite{InsightJournalWebSite} which include the 
template code to build wrappers is available at
\url{http://voxel.jouy.inra.fr/darcs/contrib-itk/template/}. Just use the command
{\em darcs get http://voxel.jouy.inra.fr/darcs/contrib-itk/template/ contribName}
and edit the project name in the {\em CMakeLists.txt} file to
begin your new contribution.} for example, is to build {\em all}
the methods of the wrapped classes, and so to be sure everything builds as it should
\footnote{We have found and fixed numbers of bug in ITK while adding
more classes to WrapITK}.
In WrapITK, we used them to avoid managing switches if some dependencies or not
found: the project must found its dependencies or fail.
